comgen-outline

### 2017-09-01 paper/comgen-paper.Rmd
more of sophies feedback from into to expt 1b

Knowing that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be necessary to thrive in our open-ended world.
Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or rare (e.g., understanding that lightning strikes tall objects).
It thus is crucial that language allow us to communicate such *generalizations* to each other.
By sharing generalizations we flourish collectively without individually needing to taste each potentially-poisonous plant or witness enough lightning strikes.
Furthermore, communicating generalizations from one generation to the next may be a foundational mechanism behind the faithful transmission of knowledge necessary for cumulative cultural evolution [@Tomasello1999; @Henrich2015].

@@

To test our model, we examine endorsements of generalizations in three domains: categories, events, and causes.
Our model makes predictions about how endorsements should vary according to (i) the listener's world knowledge prior and (ii) the speaker's state of knowledge (or, belief distribution) that she seeks to communicate. 
In Section 3, we describe experiments the measure both quantities and relate them via our model to the endorsements of generalizations about categories, or *generic language*. 
In Section 4, we describe experiments that manipulate the speaker's state of knowledge in communicating generalizations about events, or *habitual language*.
In Section 5, we describe experiments that manipulate both the listener's relevant prior knowledge and the speaker's state of knowledge in communicating generalizations about causes, or *causal language*. 
Across all of our experimental settings, we find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements (cumulative $r^2(N) = 0.XX$), where simpler models fall short.
In the final section of the paper, we discuss how our model begins the process of unifying the extant psychological, linguistic, and philosophical literatures on *genericity*.
Our theory also opens up a number of new directions for understanding generalizations in language and building models that learn from language in the way that people learn from language.

@@

Generalization from examples shows complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place.
For instance, observing that an indigenous person living on a remote island *is brown and obese* provides considerably more information about the skin color of other islanders than about their weight [@Nisbett1983].
This subtlety can be modeled by incorporating heiarchical structure into the prior belief distribution of a Bayesian model, allowing the model to represent and reason flexibly about different kinds of properties [@Kemp2008].
Observations that are generated by an intentional agent can lead to similarly subtle inferences, like unconfounding otherwise ambiguous causal evidence [@Goodman2009].

@@

To answer this, we draw a metaphor to Bayesian statistics and data analysis.
When there is a latent parameter the Bayesian scientist knows little about, she puts a prior distribution over the parameter and infers the parameter's likely value by collecting data.
In a similar vein, we posit that the meaning of a generalization in language is *underspecified*; that is, there is not a fixed $\theta$ that corresponds to the generalization, but rather the listener has uncertainty over $\theta$---in the form of a prior distribution $P(\theta)$---and infers $\theta$ after hearing an utterance.
Though it is possible different $P(\theta)$ could be learned for different contexts, we assume this prior is identical across contexts and is completely uninformed by the context: $P(\theta) = \text{Uniform}(0, 1)$.

@@

Equation \ref{eq:L0} is a model of a Bayesian listener $L$ who updates her beliefs about the prevalence $h$ according the meaning of an utterance $u$.
$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule and represents the literal semantic content of an utterance.
$P(h)$ represents the listener's prior world knowledge concerning the relevant prevalences $h$.
The particular form of the **prevalence prior** $P(h)$ plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [@Griffiths2005; @Tenenbaum2006; @Kemp2008].
This component of the model provides a potential bridge to conceptual accounts of generics [e.g., @Leslie2007; @Prasada2006; @Prasada2013].
Contrary to these accounts, in our model, conceptual structure is represented in listeners' knowledge of the world $P(h)$ and not in the semantic content of the utterance $u_{gen}$.

@@

The pair of speaker-listener models presented above correspond to the simplest possible communicative models with an underspecified threshold-meaning for a generalization. 
The *simple but underspecified* hypothesis defines a *family* of models, however, with potentially more levels of recursion (e.g., a listener who thinks about a speaker who thinks about a listener).
These are not of primary theoretical interest to this paper, as *any* formal model that explains the flexible endorsement patterns of generalizations in language will be a substantial advancement.
However, there are interesting theoretical differences to be found within this family of models (e.g., if the inference about the threshold can be thought of as a *pragmatic inference* or just a mere *literal inference*).
We discuss these alternative formulations and provide formal model comparison between these RSA models in Appendix.

@@

Next, we consider a few classic cases from the literature on generics to demonstrate the kind of inferences our listener model would draw from different generic statements.
The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$.
In Figure\ \@ref(fig:simulations) (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high prevalence values; this sort of prior could be over the prevalence of the feature "barks" because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats) and *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
The fixed threshold model (right column) struggles to differentiate those that generally do not have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.^[
We model "those that do not generally have the feature" as a Beta distribution with an expected value (mean) close to zero. 
The fact that this component of the prior is not just a Delta function at 0\% reflects the intuitive possibility that some members of a kind who do not generally have the feature (e.g., a cat who barks) could somehow acquire the feature from accidental or transient causes (e.g., a strange genetic mutation).
]
The uncertain threshold model, however, easily rules out the categories that do not generally have the feature and strongly signals the property is widespread in the category.

@@

Finally, we look at how the uncertain threshold produces an interpretation for the statement "Mosquitos carry malaria", which intuitively should correspond to "Some mosquitos carry malaria".
The prior $P(h_\text{carry malaria})$ assumes that most creatures do not carry malaria and among those that do, the feature is not very widespread.
Here, we see that listener's posterior upon hearing the generalization (the uncertain threshold) is similar to what she learns about hearing "Some mosquitos carry malaria" (the fixed threshold; Figure\ \@ref(fig:simulations) row 4). 
Thus, a speaker who believes that *very few* mosquitos carry malaria will still endorse "Mosquitos carry malaria".

In sum, these simulations show that the behavior of the uncertain-threshold semantics is distinct from both the prior distribution over probability $h$ as well as the inferences derived from a fixed-threshold semantics.
For these simulations, we had specify the prevalence prior $P(h)$.
In the rest of this paper, we both meausure and manipulate $P(h)$ and examine the behavior of the speaker model in three case studies: generalizations about categories, events, and causes.

@@

Generalizations about categories (i.e., *generic language*; e.g., *Birds fly.*) have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propogation [@Rhodes2012], and motivation [@Cimpian2007], as well as many other facets of everyday cognition.
It is the premier case study of generalizations in language because of its close relation to quantified statements (e.g., *Most birds fly*) and has received the most attention from philosophers, linguists, and psychologists.

Any theory of generic language must explain its puzzling flexibility of usage with respect to prevalence.
That is, \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} are reasonable things to say, but \emph{Birds are female} is not.
As a first test of our theory, we wish to explain the flexibility in endorsements of generics (e.g., "Birds lay eggs" vs. "Birds are female"; "Mosquitos carry malaria") in terms of the relevant prior knowledge about properties, as explored through simulation in the **Model predictions** section.
We validate these simulations empirically by measuring the prior belief distribution over the relevant probabilities $P(h)$ used in Eq. \ref{eq:L0} and the prevalence of the category that the speaker model seeks to convey (the *referent-category* prevalence) $h$ in Eq. \ref{eq:S1} (Expt. 1a).

<!-- The pragmatic speaker model $S_2$, Eq.~\ref{eq:S2}, is a model of truth judgments.  -->
We test our model on thirty generic sentences that cover a range of conceptual distinctions discussed in the literature [@Prasada2013]: characteristic (e.g. \emph{Ducks have wings.}), minority (e.g. \emph{Robins lay eggs.}), striking (e.g. \emph{Mosquitos carry malaria.}), false generalization (e.g. \emph{Robins are female.}), and false (e.g. \emph{Lions lay eggs.}).
In additional to the canonical cases from the linguistics literature, we selected sentences to elicit the full range of acceptability judgments (intuitively: "acceptable", "unacceptable", and "indeterminate") with low-, medium-, and high-prevalence properties.

To compare the model to empirical truth judgments, we measure the prior distribution over prevalence of these properties (Expt. 1a).
We hypothesize that these prior distributions encode probabilities associated with conceptual distinctions [@Prasada2013].
In particular, we hypothesize that different kind--property relations [e.g., *principled* v. *accidental relations*^[This is sometimes referred to as "statistical" relations.]; @Prasada2013] can be observed in the prevalence prior. 
If, in fact, the prevalence prior is a manifestation of deeper, conceptual knowledge, we would expect the prevalence prior data to follow a multi-modal, mixture distribution where there exist qualitatively distinct modes or components to the prior, as probabilistic traces of the different types of kinds with respect to the property.
This is important because it is one way in which our formal theory connects to other psychological accounts of generic language [cf., @Prasada2013; @Gelman2003; @Leslie2007].
As a simple test of this hypothesis---that the prevalence prior encodes conceptual knowledge---we compare a structured (i.e., mixture) model of the prior data to an unstructured one.

@@

The prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the prevalence of a given property (e.g. \textsc{lays eggs}) across relevant categories. 
To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon). Ask yourself "is it female?" Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female peregrine falcons, i.e., 50\%). Now, do you think it lays eggs? Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; If you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young. That is, the answer is either 50\% or 0\% depending on the kind of creature we are thinking of. ^[
The subjective probability may, in fact, be non-zero in what we're calling as 0\%, non-zero but very small. This would allow for the intuitive possibility of a dog that lays eggs potentially due to some strange generic mutation or the interaction of dog genetics with a foreign environment. 
].

This thought experiment decomposes the prevalence prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the prevalence of the feature given the kind $P(h \mid k)$.
We will use this decomposition to measure the prevalence prior $P(h) = \int_{k} P(h \mid k) \diff k$, and perform a structured Bayesian data-analysis to model the prior data.
We measured prior distributions empirically for the set of properties (e.g. \textsc{lays eggs, carries malaria}; 21 in total) used in our generic sentences.
After measurement, we show that assuming a structured model of the prior data is substantially preferred to an unstructured model.

@@

We recruited 60 participants over Amazon's crowd-sourcing platform Mechanical Turk (MTurk).  
Participants were restricted to those with US IP addresses and with at least a 95\% MTurk work approval rating (the same criteria apply to all experiments reported). 
3 participants were accidentally allowed to complete the experiment for a second time; we excluded their second responses (resulting in $n=57$).
2 participants self-reported a native language other than English; removing their data ($n=55$) has no effect on the results reported. 
The experiment took about 10 minutes and participants were compensated \$1.00.

@@

On each trial of the experiment, participants filled out a table where each row was an animal category and each column was a property. 
Participants first were shown six animal categories randomly sampled from a set corresponding to the generic sentences used in Expt. 1b (e.g. \textsc{robins, mosquitos}) and asked to generate five of their own.

A column then appeared to the right of the animal names with a property in the header (e.g., "lays eggs").
Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%").
Eight property--columns appeared in the table, and this whole procedure was repeated 2 times.
In total, each participant generated 10 animal names and reported on the prevalence of sixteen properties for 22 animals (their own 10 and the experimentally-supplied 12). 
<!-- For a full list of the properties, and generic sentences used in Expt. 1b, see Table 2 (Appendix). -->

@@

To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").
In analyzing the prevalence prior data, we are primarily interested in exploring the hypothesis that the prior is structured as a result of deeper conceptual knowledge.
We formalize this hypothesis using a simple Bayesian mixture model. 
We test the simplest "structural" hypothesis, where there are two, qualitatively different components to the prior [e.g., if participants believe that some kinds have a causal mechanism that *could* give rise to the property, while kinds others do not; cf., @Griffiths2005].
The "unstructured" alternative hypothesis is that there is just a single distribution that gives rise to the prevalence prior data.

For the structural hypothesis, we assume the data was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D}_{stable}$) and a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D}_{transient}$).
The "transient" distribution intuitively corresponds to accidental causes of the feature (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
We model this distribution as a Beta distribuition that heavily favors probabilities near 0: $\text{Beta}(\gamma = 0.01, \delta = 100)$.^[
Note that we use the noncanonical mean $\gamma$ and concentration $\xi$ (or, inverse-variance) parameterization of the Beta distribution rather than the canonical shape (or pseudocount) parameterization for ease of posterior inference. The shape parameterization can be recovered using: $\alpha = \gamma \cdot \xi; \beta = (1 - \gamma) \cdot \xi$.
]
The "stable" distribution is modeled as a Beta distribution with unknown parameters $\text{Beta}(\gamma, \xi)$.^[
Because the Beta distribution is not defined at the points 0 and 1, we add $\epsilon$ to the 0 responses and round 1 to 0.99.
Adjusting 1 to $1- \epsilon$ leads to improper inferences for this model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; this would disproportionately influence the shape of $\mathcal{D}_{stable}$. 
This problem does not appear for 0 being adjusted to $\epsilon$ because the "transient" distribution already expects such low values.
Similar results can be obtained by rounding 0 to 0.01. 
Alternatively, the "transient" distribution could be defined as a Delta distribution at 0, and 0 responses could remain in their raw form.
]
Finally, we assume that these two components combine with mixture weighting $\phi$ such that the data we observe is $$P(d) = \phi\cdot \text{Beta} (d \mid \gamma, \xi) + (1 -  \phi) \cdot \text{Beta}(d \mid \gamma = 0.01, \xi = 100) $$.
The unstructured alternative hypothesis assumes the data was generated by a single component in the prior distribution with unknown parameteres $P(d) = \text{Beta} (d \mid \gamma, \xi)$.

@@

Each property (e.g., "lays eggs", "carries malaria") is modeled independently (i.e., each property's prevalence prior has its own parameters).

@@

It is possible that the data is, in fact, more structured than our simple two-component model would allow. 
To see how well the structured model fits the prevalence prior data, we use Bayesian inference to infer the likely values of the parameters and then use the inferred parameters to generate new data.
This is called the *posterior predictive distribution* and is an important step in model validation. 
If the model is a good representation of the data, the posterior predictive data will align with the observed experimental data. 
We construct a posterior predictive distribution by "forward sampling" the model.^[
This can be described by the following algorithm: First, flip a coin weighted by $\phi$.
If it comes up heads, we then sample from the "stable" component: $\text{Beta}(\gamma, \xi)$.
If it comes up tails, we sample from the "transient" component: $\text{Beta}(0.01, 100)$.
We do this many times using the posterior distibution to generate a distribution over predicted prevalence ratings.
]

We implemented this statistical model using the probabilistic programming language WebPPL [@dippl].
To learn about the credible values of the parameters, we ran separate MCMC chains for each item, collecting 75,000 samples, removing the first 25,000 for burn-in.
Eight example prior distributions inferred using both the structured and unstructured models, together with the raw empirical distributions, are shown in Figure \ref{fig:generic-endorsement-priors-figure}.
There is a lot of diversity in the shapes of the distributions, which the structured model accounts for quite well.
One item that the structured model doesn't perfectly capture is the prior distribution over "lays eggs".
The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
Similar phenomena have been observed in other prevalence elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of Robins that lay eggs; @Prasada2013]
]; our simple two-component mixture model has no way to account for such a tri-modal distribution. 
A more complex model (i.e., one with three mixture components) is necessary to perfectly account for this item's data; however, we retain the imperfect simpler model for data-analytic ease going forward.

@@

The prevalence prior distribution $P_f(h)$ encodes beliefs about the prevalence (or, probabilities) of a feature $f$ across different kinds.
These distributions are structured and must be represented by a model with at least two distinct generative components: one corresponding to those kinds that only accidentally or transiently have the feature and one corresponding to those kinds with a stable causal mechanism that gives rise to the feature with some probability.

>>>>

Knowing that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be necessary to thrive in our open-ended world.
Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or rare (e.g., understanding that lightning strikes tall objects).
It thus is crucial that language allow us to communicate such *generalizations* to each other.
By sharing generalizations, we flourish collectively without individually needing to taste  potentially-poisonous plants or personally witness enough lightning strikes.
Furthermore, communicating generalizations from one generation to the next may be a foundational mechanism behind the faithful transmission of knowledge necessary for cumulative cultural evolution [@Tomasello1999; @Henrich2015].

@@

To test our model, we examine endorsements of generalizations in three domains: categories, events, and causes.
Our model makes predictions about how endorsements should vary according to (i) the listener's prior world knowledge and (ii) the speaker's state of knowledge (or, belief distribution) that she seeks to communicate. 
In Section 3, we describe experiments that measure both quantities and relate them via our model to the endorsements of generalizations about categories (*generic language*). 
In Section 4, we describe experiments that manipulate the speaker's state of knowledge in communicating generalizations about events (*habitual language*).
In Section 5, we describe experiments that manipulate both the listener's relevant prior knowledge and the speaker's state of knowledge in communicating generalizations about causes (*causal language*).

Across all of our experimental settings, we find a very strong agreement of our model's predictions to the full spectrum of human elicited endorsements (cumulative $r^2(N) = 0.XX$), where simpler models fall short.
In the final section of the paper, we discuss how our model paves a path to unifying the extant psychological, linguistic, and philosophical literatures on *genericity*.
Our theory also opens up a number of new directions for understanding generalizations in language and building models that learn from language in the way that people learn from language.

@@

Generalization from examples shows complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place.
For instance, observing that an indigenous person living on a remote island *is brown and obese* provides considerably more information about the skin color of other islanders than about their weight [@Nisbett1983].
This subtlety can be modeled by incorporating heiarchical structure into the prior belief distribution of a Bayesian model, allowing the model to represent and reason flexibly about different kinds of properties [@Kemp2008].
Observations that are generated by an intentional agent can lead to similarly subtle inferences, like deconfounding otherwise ambiguous causal evidence [@Goodman2009].

@@

To answer this, we draw a metaphor to Bayesian statistics and data analysis.
When there is a latent parameter the Bayesian scientist knows little about, she puts a prior distribution over the parameter and infers the parameter's likely value by collecting data.
In a similar vein, we posit that the meaning of a generalization in language is *underspecified*; that is, there is not a fixed $\theta$ that corresponds to the generalization, but rather the listener has uncertainty over $\theta$---in the form of a prior distribution $P(\theta)$---and infers $\theta$ after hearing an utterance.
Though it is possible that different $P(\theta)$s could be learned for different contexts, we assume this prior is identical across contexts and is completely uninformed by the context: $P(\theta) = \text{Uniform}(0, 1)$.

@@

Equation \ref{eq:L0} is a model of a Bayesian listener $L$ who updates her beliefs about the prevalence $h$ according to the meaning of an utterance $u$.
$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule and represents the literal semantic content of an utterance.
$P(h)$ represents the listener's prior world knowledge concerning the relevant prevalences $h$.
The particular form of the **prevalence prior** $P(h)$ plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [@Griffiths2005; @Tenenbaum2006; @Kemp2008].
This component of the model provides a potential bridge to conceptual accounts of generics [e.g., @Leslie2007; @Prasada2006; @Prasada2013].
Contrary to these accounts, in our model, conceptual structure is represented in listeners' knowledge of the world $P(h)$ and not in the semantic content of the utterance $u_{gen}$.

@@

The pair of speaker-listener models presented above correspond to the simplest possible communicative models with an underspecified threshold-meaning for a generalization. 
The *simple but underspecified* hypothesis defines a *family* of models, however, with potentially more levels of recursion (e.g., a listener who thinks about a speaker who thinks about a listener).
To our knowledge there is no unifying computational account of linguistic genericity and as such, the primary theoretical interest of this paper is to outline such an account, rather than discuss possible variations within it. 
However, there are interesting theoretical differences to be found within this family of models (e.g., if the inference about the threshold can be thought of as a *pragmatic inference* or just a mere *literal inference*).
We discuss these alternative formulations and provide formal model comparison between these RSA models in the Appendix.

@@

Next, we consider a few classic cases from the literature on generics to demonstrate the kind of inferences our listener model would draw from different generic statements.
The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$.
In Figure\ \@ref(fig:simulations) (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high prevalence values; this prior could be over the prevalence of the feature *barks* because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats), but *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
The fixed threshold model (right column) struggles to differentiate those that generally do not have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.^[
We model "those that do not generally have the feature" as a Beta distribution with an expected value (mean) close to zero. 
The fact that this component of the prior is not just a Delta function at 0\% reflects the intuitive possibility that some members of a kind who do not generally have the feature (e.g., a cat who barks) could somehow acquire the feature from accidental or transient causes (e.g., a strange genetic mutation).
]
The uncertain threshold model, however, easily rules out the categories that do not generally have the feature and strongly signals the property is widespread in the category.

@@

Finally, we look at how the uncertain threshold produces an interpretation for the statement "Mosquitos carry malaria", which intuitively should correspond to "Some mosquitos carry malaria".
The prior $P(h_\text{carry malaria})$ assumes that most creatures do not carry malaria and among those that do, the feature is not very widespread.
Here, we see that listener's posterior upon hearing the generalization (the uncertain threshold) is similar to what she learns upon hearing "Some mosquitos carry malaria" (the fixed threshold; Figure\ \@ref(fig:simulations) row 4). 
Thus, a speaker who believes that *very few* mosquitos carry malaria will still endorse "Mosquitos carry malaria".

In sum, these simulations show that the behavior of the uncertain-threshold semantics is distinct from both the prior distribution over probability $h$, as well as the inferences derived from a fixed-threshold semantics.
For these simulations, we had specify the prevalence prior $P(h)$.
In the rest of this paper, we both meausure and manipulate $P(h)$ and examine the behavior of the speaker model in three case studies: generalizations about categories, events, and causes.

@@

Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propogation [@Rhodes2012], and motivation [@Cimpian2007], as well as many other facets of everyday cognition.
It is the premier case study of generalizations in language because of its close relation to quantified statements (e.g., "Most dogs bark") and has received the most attention from philosophers, linguists, and psychologists.

Any theory of generic language must explain its puzzling flexibility of usage with respect to prevalence.
That is, "Mosquitos carry malaria" and "Birds lay eggs" are reasonable things to say, but "Birds are female" is not.
As a first test of our theory, we wish to explain the flexibility in endorsements of generics in terms of the relevant prior knowledge about properties, as explored through simulation in the **model simulations** section.
We validate these simulations empirically by measuring the prior belief distribution over the relevant probabilities $P(h)$ used in Eq. \ref{eq:L0} and the prevalence of the category that the speaker model seeks to convey (the *referent-category* prevalence) $h$ in Eq. \ref{eq:S1} (Expt. 1a).

<!-- The pragmatic speaker model $S_2$, Eq.~\ref{eq:S2}, is a model of truth judgments.  -->
We test our model on thirty generic sentences that cover a range of conceptual distinctions discussed in the literature [@Prasada2013]: *characteristic* (e.g., "Ducks have wings."), *minority* (e.g., "Robins lay eggs."), *striking* (e.g. "Mosquitos carry malaria."), *false generalization* (e.g., "Robins are female."), and *absent features* (e.g. "Lions lay eggs.").
In additional to the canonical cases from the linguistics literature, we select sentences to elicit the full range of acceptability judgments (intuitively: "acceptable", "unacceptable", and "indeterminate") with low-, medium-, and high-prevalence properties.

To compare the model to empirical truth judgments, we measure the prior distribution over prevalence of these properties (Expt. 1a).
We hypothesize that these prior distributions encode probabilities associated with conceptual distinctions [@Prasada2013].
In particular, we hypothesize that different kind--property relations [e.g., *principled* v. *accidental relations*^[This is sometimes referred to as "statistical" relations.]; @Prasada2013] can be observed in the prevalence prior. 
If, in fact, the prevalence prior is a manifestation of deeper, conceptual knowledge, we would expect the prevalence prior data to follow a multi-modal, mixture distribution where there exist qualitatively distinct modes or components to the prior, as probabilistic traces of the different types of kinds with respect to the property.
A prior that is structured would be one way in which our formal theory connects to other psychological accounts of generic language [cf., @Prasada2013; @Gelman2003; @Leslie2007].
As a simple test of this hypothesis---that the prevalence prior encodes conceptual knowledge---we compare a structured (i.e., mixture) model of the prior data to an unstructured one.

@@

The prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the prevalence of a given property (e.g. \textsc{lays eggs}) across relevant categories. 
To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon). Ask yourself "is it female?" Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female peregrine falcons, i.e., 50\%). Now, do you think it lays eggs? Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; if you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young. That is, the answer is either 50\% or 0\% depending on the kind of creature you are thinking of^[
The subjective probability may, in fact, be non-zero and small for what we're calling 0\%. 
Non-zero probabilities allow for the intuitive possibility of a dog that lays eggs potentially due to some strange generic mutation or the interaction of dog genetics with a strange environment. 
].

This thought experiment decomposes the prevalence prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the prevalence of the feature given the kind $P(h \mid k)$.
We will use this decomposition to measure the prevalence prior $P(h) = \int_{k} P(h \mid k) \diff k$, and perform a structured Bayesian data-analysis to model the prior data.
We measured prior distributions empirically for the set of properties (e.g., \textsc{lays eggs, carries malaria}; 21 in total) used in our generic sentences.
After measurement, we show that assuming a structured model of the prior data is substantially preferred to an unstructured model.

@@

We recruited 60 participants over Amazon's crowd-sourcing platform Mechanical Turk (MTurk).  
Participants were restricted to those with US IP addresses and with at least a 95\% MTurk work approval rating (the same criteria apply to all experiments reported). 
Three participants were accidentally allowed to complete the experiment for a second time, so we excluded their second responses (resulting in $n=57$).
Two participants self-reported a native language other than English; removing their data ($n=55$) has no effect on the results reported. 
The experiment took about 10 minutes and participants were compensated \$1.00.

@@

On each trial of the experiment, participants filled out a table where each row was an animal category and each column was a property. 
Participants first were shown six animal categories randomly sampled from a set corresponding to the generic sentences used in Expt. 1b (e.g., \textsc{robins, mosquitos}) and were asked to generate five of their own.

A column then appeared to the right of the animal names with a property in the header (e.g., *lays eggs*).
Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%").
Eight property--columns appeared in the table, and this whole procedure was repeated two times.
In total, each participant generated ten animal names and reported on the prevalence of sixteen properties for twenty-two animals (their own ten and the experimentally-supplied twelve). 
<!-- For a full list of the properties, and generic sentences used in Expt. 1b, see Table 2 (Appendix). -->

@@

To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").
In analyzing the prevalence prior data, we are primarily interested in exploring the hypothesis that the prior is structured as a result of deeper conceptual knowledge.
We formalize this hypothesis using a simple Bayesian mixture model. 
We test the simplest "structural" hypothesis, where there are two, qualitatively different components to the prior [e.g., if participants believe that some kinds have a causal mechanism that *could* give rise to the property, while other kinds do not; cf., @Griffiths2005].
The "unstructured" alternative hypothesis is that there is just a single distribution that gives rise to the prevalence prior data.

For the structured hypothesis, we assume the data was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D}_{stable}$) and a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D}_{transient}$).
The "transient" distribution intuitively corresponds to accidental causes of the feature (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
We model this distribution as a Beta distribuition that heavily favors probabilities near 0: $\text{Beta}(\gamma = 0.01, \delta = 100)$.^[
Note that we use the noncanonical mean $\gamma$ and concentration $\xi$ (or, inverse-variance) parameterization of the Beta distribution rather than the canonical shape (or pseudocount) parameterization for ease of posterior inference. The shape parameterization can be recovered using: $\alpha = \gamma \cdot \xi; \beta = (1 - \gamma) \cdot \xi$.
]
The "stable" distribution is modeled as a Beta distribution with unknown parameters $\text{Beta}(\gamma, \xi)$.^[
Because the Beta distribution is not defined at the points 0 and 1, we add $\epsilon$ to the 0 responses and round 1 to 0.99.
Adjusting 1 to $1- \epsilon$ leads to improper inferences for this model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; treating 1 as $1- \epsilon$ disproportionately influences the shape of $\mathcal{D}_{stable}$ relative to other responses.
This problem does not appear for 0 being adjusted to $\epsilon$ because the "transient" distribution already expects such low values.
Similar results can be obtained by rounding 0 to 0.01. 
Alternatively, the "transient" distribution could be defined as a Delta distribution at 0, and 0 responses could remain in their raw form.
]
Finally, we assume that these two components combine with mixture weighting $\phi$ such that the data we observe is $$P(d) = \phi\cdot \text{Beta} (d \mid \gamma, \xi) + (1 -  \phi) \cdot \text{Beta}(d \mid \gamma = 0.01, \xi = 100) $$.
The unstructured alternative hypothesis assumes the data was generated by a single component in the prior distribution with unknown parameteres $P(d) = \text{Beta} (d \mid \gamma, \xi)$.

@@

Each property (e.g., *lays eggs*, *carries malaria*) is modeled independently (i.e., each property's prevalence prior has its own parameters).

@@

It is possible that the data is, in fact, more structured than our simple two-component model would allow. 
To see how well the structured model fits the prevalence prior data, we use Bayesian inference to infer the *a posteriori* likely values of the parameters and then use the inferred parameters to generate new data.
The generated data from the model's posterior is called the *posterior predictive distribution* and is an important step in model validation. 
If the model is a good representation of the data, the posterior predictive data will align with the observed experimental data. 
We construct a posterior predictive distribution by "forward sampling" the model.^[
This can be described by the following algorithm: First, flip a coin weighted by $\phi$.
If it comes up heads, we then sample from the "stable" component: $\text{Beta}(\gamma, \xi)$.
If it comes up tails, we sample from the "transient" component: $\text{Beta}(0.01, 100)$.
We do this many times using the posterior distibution to generate a distribution over predicted prevalence ratings.
]

To learn about the credible values of the parameters, we ran separate MCMC chains for each item, collecting 75,000 samples, removing the first 25,000 for burn-in.
Eight example prior distributions inferred using both the structured and unstructured models, together with the raw empirical distributions, are shown in Figure \ref{fig:generic-endorsement-priors-figure}.
There is a lot of diversity in the shapes of the distributions, which the structured model accounts for quite well.
One item that the structured model doesn't perfectly capture is the prior distribution over "lays eggs".
The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
Similar phenomena have been observed in other prevalence elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of *robins* that *lay eggs*; @Prasada2013]
]; our simple two-component mixture model has no way to account for such a tri-modal distribution. 
A more complex model (i.e., one with three mixture components) is necessary to perfectly account for this item's data; however, we retain the imperfect simpler model for data-analytic ease going forward.

@@

The prevalence prior distribution $P_f(h)$ encodes beliefs about the prevalence (or, probabilities) of a feature $f$ across different kinds.
These distributions are structured and are best represented by a model with at least two distinct generative components: one corresponding to those kinds that only accidentally or transiently have the feature and one corresponding to those kinds with a stable causal mechanism that gives rise to the feature with some probability.
